---
title: "Annex B · R Functions Tutorial"
---

[under construction] A quick-reference tutorial for the R functions used across all four lectures.

## Loading packages

```{r}
#| eval: false
library(psych)   # fa()
library(lavaan)  # cfa(), sem()
```

## Function reference

| Function | Package | What it does |
|---|---|---|
| `fa()` | psych | Fits an exploratory factor analysis with a chosen rotation |
| `cfa()` | lavaan | Fits a confirmatory factor analysis from model syntax |
| `sem()` | lavaan | Fits a full structural equation model (measurement + structural) |
| `summary()` | lavaan | Prints fit measures and parameter estimates for a fitted model |
| `standardizedSolution()` | lavaan | Extracts standardized loadings and paths as a data frame |
| `modificationIndices()` | lavaan | Flags parameters that would most improve fit if freed |

## Worked snippet

```{r}
#| eval: false
fit <- sem(sem_model, data = lvm_data)
summary(fit, standardized = TRUE, fit.measures = TRUE)
standardizedSolution(fit)
```

::: {.callout-tip}
Run `standardizedSolution()` before reporting any loading — raw lavaan output is unstandardized by default.
:::
